Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2020-09-22 Scripts/Initial_Analysis.Rmd
Vulnerabillity index

@@

@@

  map <- World_eez_sf %>% 
    left_join(Eez_d_hist,
              by = "eezid") %>% 
    filter(tresh == tresh_list[i],
           metric == "mean_yr") %>% 
    ggplot() +
    geom_sf(
      aes(
        fill = reverse
      ),
      color =  "white",
      size = 0.1
    ) +
    # Inlcude the participation of species
    geom_sf(data = World_map_part,
            aes(fill = participation+2000),
            color =  "white",
            size = 0.1
            ) +
    # grey maps
    geom_sf(data = grey_land, aes(),fill = "grey50", color =  "white",size = 0.1) +
    geom_sf(data = grey_eez, aes(),fill = "grey50", color =  "white",size = 0.1) +
    # Set Participation labels
    annotate("text", 
             x =-135,
             y = -69,
             label = "Participation (%)", 
             color="black", 
             size=4, 
             angle=0, 
             fontface="bold",
             hjust=0) +
    annotate("text", 
             x = c(-76,-35,6,48,88),
             y = -69,
             # x =(c(-8500000,-3000000,2500000,7500000,12800000)),
             # y = -9050000,
             label = c(0,25,50,75,100), 
             color="black", 
             size=4, 
             angle=0, 
             # fontface="bold",
             hjust=0) +
    # Set ToE labels
    annotate("text", 
             x =-135,
             y = -85,
             label = "Time of Emergence",
             color="black", 
             size=4, 
             angle=0, 
             fontface="bold",
             hjust=0) +
    annotate("text", 
             x = c(-79,-39,3,45,87),
             y = -85,
             label = seq(2100,2000,-25), 
             color="black", 
             size=4, 
             angle=0, 
             # fontface="bold",
             hjust=0) +
    scale_fill_viridis("",
      limits = c(2000,2100),
      breaks = seq(2000,2100,25),
      labels = c("","","","","")#,
      # direction = -1
    ) +
    # geom_hline(yintercept = c(-50,0,50,80)) +
    my_ggtheme_m() +
    theme(
      legend.box.margin = margin(t = -64, l = 229),
      legend.text = element_blank(),
      legend.key.width = unit(5, "line")
    )

>>>>

```{r vulnerabillity_index, eval = T}

# Per EEZs
Eez_d_hist <- Eme_Res %>% 
  group_by(eezid ,sau_fishing_entity,fishing_entity_id,tresh) %>% 
  # summarise(n_tax = length(unique(taxon_key))) %>% 
  summarise(
    mean_yr = mean(emerging_yr,na.rm=T),
    sd_yr = sd(emerging_yr,na.rm=T),
    n_taxa = length(unique(taxon_key))
    ) %>% 
  gather("metric","value",mean_yr:n_taxa) %>% 
  # filter(metric != "n_taxa") %>% 
  mutate(
    reverse = abs(value-2100)  + 2000
  ) %>% 
  filter(
    tresh == "Tresh_one",
    metric == "mean_yr"
  )

Value_map_data <- Eme_value_data %>% 
  left_join(Total_value,
            by = c("fishing_entity_id","variable")) %>% 
  mutate(participation = (sum_value/tot_value)*100) %>% 
  filter(
    tresh == "Tresh_one",
    variable == "value"
  )

@@

### ----------------- ###
### Index alternative ###
### ----------------- ###

Index_data <- Eez_d_hist %>% 
  left_join(Value_map_data) %>% 
  mutate(
    index = (participation/value),
    index = ifelse(is.na(index),0,index)
  ) %>% 
  select(1:3,value,participation,index,everything())

##### Normalize index
# https://www.datanovia.com/en/blog/how-to-normalize-and-standardize-data-in-r-for-great-heatmap-visualization/

# Get min and maximums
min_index <- min(Index_data$index)
max_index <- max(Index_data$index)

Index_data <- Index_data %>% 
  mutate(
    index = 2000 + (index-min_index)*(2100-2000)/(max_index-min_index)
  )

Value_map_data <- Index_data %>% 
  select(sau_fishing_entity,fishing_entity_id,tresh,variable,participation = indexb)

### ----------------- ###

@@

  map <- World_eez_sf %>% 
    left_join(Eez_d_hist,
              by = "eezid") %>% 
    filter(tresh == tresh_list[i],
           metric == "mean_yr") %>% 
    ggplot() +
    geom_sf(
      aes(
        fill = reverse #original map
        # fill = value
      ),
      color =  "white",
      size = 0.1
    ) +
    # Inlcude the participation of species
    geom_sf(data = World_map_part,
            # aes(fill = participation+2000), #original map
            aes(fill = participation),
            color =  "white",
            size = 0.1
            ) +
    # grey maps
    geom_sf(data = grey_land, aes(),fill = "grey50", color =  "white",size = 0.1) +
    geom_sf(data = grey_eez, aes(),fill = "grey50", color =  "white",size = 0.1) +
    # Set Participation labels
    annotate("text",
             x =-135,
             y = -69,
             label = "Vulnerabillity index",
             color="black",
             size=4,
             angle=0,
             fontface="bold",
             hjust=0) +
    annotate("text", 
             x = c(-76,-35,6,48,88),
             y = -69,
             # x =(c(-8500000,-3000000,2500000,7500000,12800000)),
             # y = -9050000,
             label = c(0,25,50,75,100), 
             color="black", 
             size=4, 
             angle=0, 
             # fontface="bold",
             hjust=0) +
    # Set ToE labels
    annotate("text", 
             x =-135,
             y = -85,
             label = "Time of Emergence",
             color="black", 
             size=4, 
             angle=0, 
             fontface="bold",
             hjust=0) +
    annotate("text", 
             x = c(-79,-39,3,45,87),
             y = -85,
             label = seq(2100,2000,-25), # original
             # label = seq(2000,2100,25), 
             color="black", 
             size=4, 
             angle=0, 
             # fontface="bold",
             hjust=0) +
    scale_fill_viridis("",
      limits = c(2000,2100),
      breaks = seq(2000,2100,25),
      labels = c("","","","","")#,
      # direction = -1
    ) +
    # geom_hline(yintercept = c(-50,0,50,80)) +
    my_ggtheme_m() +
    theme(
      legend.box.margin = margin(t = -64, l = 229),
      legend.text = element_blank(),
      legend.key.width = unit(5, "line")
    )
